---
title: "Homework #1 -- Pet Names Dataset"
author: "Nawaf almutairi"
date: "`r Sys.Date()`"
output: github_document
---

2210002968

**Deadline:** 23:59 on Monday, 21 March 2022


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

1.  How many pets are included in this dataset? (Simply count the number of rows)


```{r}
nrow(seattlepets)
```
Write your answer here: 52519

*Knit the document, commit your changes with a commit message that says "Completed Exercise 1", and push. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.*

2.  How many variables do we have for each pet? (Simply count the number of columns)


```{r}
ncol(seattlepets)
```
Write your answer here: 7

*Knit the document, commit your changes with a commit message that says "Completed Exercise 2", and push. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.*

3.  What are the three most common pet names in Seattle? To do this you will need to count the frequencies of each pet name and display the results in descending order of frequency so that you can easily see the top three most popular names. 


```{r}
seattlepets %>%
  count(animal_name)%>%
  arrange(desc(n))
```
Write your answer here:The most popular pet names in Seattle are Lucy With 439, Charlie With 389, and Luna With 355.

*Knit the document, commit your changes with a commit message that says "Completed Exercise 3", and push. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.*